Supplementary Material for Asymmetry paper

### 2020-07-01 Supplementary/Sup_mat.Rmd
Updated
Text and models updated

```{r PltRewardestimates, echo = F, inlude = T, warning = F, fig.asp=.75, fig.cap="_Posterior distributions for the Reward Study_"}
# get draws 
draws_df <- draws_factor(Reward_m1) %>% 
  mutate(prop = boot::inv.logit(estimate))

# make separate plots for main effects and interactions 
plt_dist <- draws_df %>% 
  ggplot(aes(prop, 
             colour = Dist_Type,
             fill = Dist_Type)) + 
  geom_density(alpha = .3) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  theme_bw() +
  guides(colour = guide_legend(title = "Distance Type"),
         fill = guide_legend(title = "Distance Type")) +
  scale_x_continuous(expression(paste("Normalised ", Delta)))

plt_gamble <- draws_df %>% 
  ggplot(aes(prop, 
             colour = Gamble_Type,
             fill = Gamble_Type)) + 
  geom_density(alpha = .3) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  theme_bw() +
  guides(colour = guide_legend(title = "Gamble Type"),
         fill = guide_legend(title = "Gamble Type")) +
  scale_x_continuous(expression(paste("Normalised ", Delta)))

plt_inter <- draws_df %>%
  ggplot(aes(prop, 
             colour = Gamble_Type,
             fill = Gamble_Type)) + 
  geom_density(alpha = .3) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  theme_bw() +
  guides(colour = guide_legend(title = "Gamble Type"),
         fill = guide_legend(title = "Gamble Type")) +
  scale_x_continuous("Normalised Position") + 
  facet_wrap(~Dist_Type)

gridExtra::grid.arrange(plt_dist, plt_gamble, plt_inter)

@@

@@

```{r ProbPriors, include = F, echo = T, cache = T}
ProbPriors_model <- brm(Ml_fix ~ (bias_type + dist_type)^2 + (dist_type * bias_type|participant),
                        data = df_model,
                        family = "bernoulli",
                        prior = Rewards_priors,
                        chains = 1,
                        iter =   n_iter,
                        warmup = n_warmup,
                        sample_prior = "only")
```

```{r ProbPriorsPlt, include = T, echo = F}
ProbPriordraws <- Prob_draws(ProbPriors_model)

plt_ProbPrior_interaction <- ProbPriordraws$plt_estimates + 
  scale_x_continuous(expression(paste("Normalised ", Delta))) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  theme_bw() + 
  guides(fill = guide_legend("Bias Type"),
         colour = guide_legend("Bias Type"))

@@

plt_ProbPrior_meDist <- prior_draws %>%
  ggplot(aes(prop,
             colour = Dist_type,
             fill = Dist_type)) + 
  geom_density(alpha = .3) + 
  theme_bw() +  
  theme(axis.title.x = element_blank()) +
  labs(fill = "Distance Type",
       colour = "Distance Type") +
  #       x = "Proportion of Fixations to Most Likely Side") +
  see::scale_color_material() + 
  see::scale_fill_material() + 
  scale_x_continuous(labels = scales::percent_format(accuracy = 1))

@@

gridExtra::grid.arrange(plt_ProbPrior_meDist, plt_ProbPrior_meBias, plt_ProbPrior_interaction)

@@

```{r ProbModel, include = F, echo = T, cache = T}
ProbModel <- brm(Ml_fix ~ (bias_type + dist_type)^2 + (dist_type * bias_type|participant),
                 data = df_model,
                 family = "bernoulli",
                 prior = Rewards_priors,
                 chains = 1,
                 iter = n_iter,
                 warmup = n_warmup)
```

```{r ProbModelPlts, include = T, echo = F}
Probdraws <- Prob_draws(ProbModel)

plt_ProbPost <- Probdraws$plt_estimates + 
  scale_x_continuous(expression(paste("Normalised ", Delta))) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  theme_bw() + 
  guides(fill = guide_legend("Bias Type"),
         colour = guide_legend("Bias Type"))
```

@@

Note: Do we want the stuff about side fixations in here?
```{r ProbModelOutputs, include = T, echo = F, fig.cap = "_Posterior predictions for the probability matching experiment_"}
# Proportion fixations to most likely side 
plt_me_Bias <- draws %>% 
  ggplot(aes(prop,
             colour = Bias_type,
             fill = Bias_type)) + 
  geom_density(alpha = .3) + 
  theme_bw() + 
  theme(axis.title.x = element_blank()) +
  labs(fill = "Bias Type",
       colour = "Bias Type") +
  #       "Proportion of Fixations to Most Likely Side") +
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  scale_x_continuous(labels = scales::percent_format(accuracy = 1))

plt_me_Dist <- draws %>% 
  ggplot(aes(prop,
             colour = Dist_type,
             fill = Dist_type)) + 
  geom_density(alpha = .3) + 
  theme_bw() +  
  theme(axis.title.x = element_blank()) +
  labs(fill = "Distance Type",
       colour = "Distance Type") +
  #       x = "Proportion of Fixations to Most Likely Side") +
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  scale_x_continuous(labels = scales::percent_format(accuracy = 1))

gridExtra::grid.arrange(plt_me_Dist, plt_me_Bias, plt_ProbPost)
```

## Discussion

>>>>

```{r setup_PltRewardestimates, echo = F, include = F, warning = F}
# get draws 
draws_df <- draws_factor(Reward_m1) %>% 
  mutate(prop = boot::inv.logit(estimate))

# make separate plots for main effects and interactions 
plt_dist <- draws_df %>%
  ggplot(aes(prop,
             colour = Dist_Type,
             fill = Dist_Type)) +
  geom_density(alpha = .3) +
  # see::scale_color_material() +
  # see::scale_fill_material() +
  scale_colour_viridis_d() + 
  scale_fill_viridis_d() +
  theme_bw() +
  guides(colour = guide_legend(title = "Distance Type"),
         fill = guide_legend(title = "Distance Type")) +
  scale_x_continuous("")

plt_gamble <- draws_df %>% 
  ggplot(aes(prop, 
             colour = Gamble_Type,
             fill = Gamble_Type)) + 
  geom_density(alpha = .3) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  theme_bw() +
  guides(colour = guide_legend(title = "Gamble Type"),
         fill = guide_legend(title = "Gamble Type")) +
  scale_x_continuous("")

plt_inter <- draws_df %>%
  ggplot(aes(prop, 
             colour = Gamble_Type,
             fill = Gamble_Type)) + 
  geom_density(alpha = .3) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  theme_bw() +
  guides(colour = guide_legend(title = "Gamble Type"),
         fill = guide_legend(title = "Gamble Type")) +
  scale_x_continuous(expression(paste("Normalised ", Delta))) + 
  facet_wrap(~Dist_Type)

# get common guide 
Reward_legend <- g_legend(plt_inter)

bottom <- grid.arrange(arrangeGrob(plt_gamble + theme(legend.position = "none"), plt_inter + theme(legend.position = "none")), 
             Reward_legend, widths=c(4.5, 1))

@@

```{r PltRewardestimates, echo = F, include = T, warning = F, fig.asp=.75, fig.cap="_Posterior distributions for the Reward Study_"}
gridExtra::grid.arrange(plt_dist, bottom, heights = c(2, 4))
```

@@

```{r ProbPriors, include = T, echo = T, message = F, warning = F, results = "hide", cache = TRUE}
ProbPriors_model <- brm(Ml_fix ~ (bias_type + dist_type)^2 + (dist_type * bias_type|participant),
                        data = df_model,
                        family = "bernoulli",
                        prior = Rewards_priors,
                        chains = 1,
                        iter =   n_iter,
                        warmup = n_warmup,
                        sample_prior = "only")
```

```{r setupProbPriorsPlt, include = F, echo = F}
ProbPriordraws <- Prob_draws(ProbPriors_model)

plt_ProbPrior_interaction <- ProbPriordraws$plt_estimates + 
  scale_x_continuous("Probability of fixating the Most likely side") +
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  theme_bw() + 
  guides(fill = guide_legend("Bias Type"),
         colour = guide_legend("Bias Type"))

@@

plt_ProbPrior_meDist <- prior_draws %>%
  ggplot(aes(prop,
             colour = Dist_type,
             fill = Dist_type)) + 
  geom_density(alpha = .3) + 
  theme_bw() +  
  theme(axis.title.x = element_blank()) +
  labs(fill = "Distance Type",
       colour = "Distance Type") +
  #       x = "Proportion of Fixations to Most Likely Side") + 
  scale_colour_viridis_d() + 
  scale_fill_viridis_d() +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1))

@@

# get common guide 
ProbPrior_legend <- g_legend(plt_ProbPrior_interaction)

bottom <- grid.arrange(arrangeGrob(plt_ProbPrior_meBias + theme(legend.position = "none"), plt_ProbPrior_interaction + theme(legend.position = "none")), 
             ProbPrior_legend, widths=c(4.5, 1))

@@

```{r ProbPriorsPlt, echo = F, fig.cap="_Prior Predictive checks for the Probability matching experiment_"}
gridExtra::grid.arrange(plt_ProbPrior_meDist, bottom, heights = c(2, 4))
```

```{r ProbModel, include = T, echo = T, message = F, warning = F, results = "hide", cache = TRUE}
ProbModel <- brm(Ml_fix ~ (bias_type + dist_type)^2 + (dist_type * bias_type|participant),
                 data = df_model,
                 family = "bernoulli",
                 prior = Rewards_priors,
                 chains = 1,
                 iter = n_iter,
                 warmup = n_warmup)
```

summary(ProbModel)$fixed

```{r getdraws, include = F, echo = F}
Probdraws <- Prob_draws(ProbModel)

@@

**Note: Do we want the stuff about side fixations in here? As in; were people more likely to fixate the side vs. centre in the bias condition?**
```{r setupProbModelOutputs, include = F, echo = F}
plt_ProbPost <- Probdraws$plt_estimates + 
  scale_x_continuous("Probability of fixating the Most likely side") + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  theme_bw() + 
  guides(fill = guide_legend("Bias Type"),
         colour = guide_legend("Bias Type"))

# Proportion fixations to most likely side 
plt_me_Bias <- draws %>% 
  ggplot(aes(prop,
             colour = Bias_type,
             fill = Bias_type)) + 
  geom_density(alpha = .3) + 
  theme_bw() + 
  theme(axis.title.x = element_blank()) +
  labs(fill = "Bias Type",
       colour = "Bias Type") +
  #       "Proportion of Fixations to Most Likely Side") +
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  scale_x_continuous(labels = scales::percent_format(accuracy = 1))

plt_me_Dist <- draws %>% 
  ggplot(aes(prop,
             colour = Dist_type,
             fill = Dist_type)) + 
  geom_density(alpha = .3) + 
  theme_bw() +  
  theme(axis.title.x = element_blank()) +
  labs(fill = "Distance Type",
       colour = "Distance Type") +
  #       x = "Proportion of Fixations to Most Likely Side") +
  scale_colour_viridis_d() + 
  scale_fill_viridis_d() + 
  scale_x_continuous(labels = scales::percent_format(accuracy = 1))

ProbPost_legend <- g_legend(plt_ProbPost)

bottom <- grid.arrange(arrangeGrob(plt_me_Bias + theme(legend.position = "none"), plt_ProbPost + theme(legend.position = "none")), 
             ProbPost_legend, widths=c(4.5, 1))
# gridExtra::grid.arrange(plt_me_Dist, plt_me_Bias, plt_ProbPost)
```

```{r ProbModelOutputs, include = T, echo = F, fig.cap = "_Posterior predictions for the probability matching experiment_"}
gridExtra::grid.arrange(plt_me_Dist, bottom,  ncol = 1, heights = c(2,4))
```

## Discussion 
The results of this study suggest that participants were in fact sensitive to the difference in probability of each side containing the target and responded by fixating this location more often when there was a bias compared to the Symmetric conditions. However, the presence of a bias did not lead participants to utilising a more optimal strategy. It would appear that the introduction of a bias for one target distracted participants from discovering the optimal strategy. Instead, participants appeared to focus primarily on the probability aspect of the task.
